---
title: "466A1"
author: "Zixuan Yuan"
date: "2023-02-02"
output:
  html_document:
    df_print: paged
---

```{r}
library(knitr)
library(tidyverse)
library(broom) 
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(ggrepel)
library(car)
library(Matrix)
library(jrvFinance)
```
#load data into R studio
```{r}
collected_data <- read.csv("select.csv")
collected_data <- na.omit(collected_data)
summary(collected_data)
```
#convert my hand collected data into date form
```{r}
collected_data$MATURITY.DATE<-as.Date(collected_data$MATURITY.DATE,"%Y/%m/%d")
collected_data$ISSUE.DATE<-as.Date(collected_data$ISSUE.DATE,"%Y/%m/%d")
```

```{r}
collected_data<-collected_data[order(collected_data$MATURITY.DATE), ]
```

```{r}
collected_data <- collected_data %>% mutate(time_till_m = difftime(MATURITY.DATE,"2023-1-16",units = "days"))
```

```{r}
collected_data$COUPON = gsub('%', '', collected_data$COUPON)
collected_data <- collected_data %>% mutate(coupon_final = (as.numeric(collected_data$COUPON))/100 )
```







```{r}

closed_p = matrix(c(collected_data$`X2023.1.16`,collected_data$`X2023.1.17`,collected_data$`X2023.1.18`,collected_data$`X2023.1.19`,
                         collected_data$`X2023.1.20`,collected_data$`X2023.1.23`,collected_data$`X2023.1.24`,collected_data$`X2023.1.25`,
                         collected_data$`X2023.1.26`,collected_data$`X2023.1.27`), nrow=10, ncol = 10, byrow=TRUE)
day_choose<-c("2023-1-16","2023-1-17","2023-1-18","2023-1-19","2023-1-20","2023-1-23","2023-1-24","2023-1-25","2023-1-26","2023-1-27")
```
#bond.TCF returns a list of three components: The accrued interest, A vector of cash flows, A vector of cash flow dates in number of years. What I need here is just the accrued interest. And then plus the accrued interest and the clean price to get the dirty price, which will be needed later. 
```{r}
price_dirty = matrix('numeric',nrow=10,ncol=10)
for(j in 1:10){
  for(i in 1:10){
    price_dirty[j,i] = bond.TCF(day_choose[j], collected_data$MATURITY.DATE[i], collected_data$coupon_final[j],
                             freq = 2)$accrued+closed_p[j,i]
  }
}
```

#Duration Between Two Dates in Fractional Year Terms can be calculated by function yearFraction in package jrvFinance
```{r}
year_fraction_matrix = matrix('numeric',nrow=10,ncol=10)
for (i in c(1:10)){
  for (j in c(1:10)){
    year_fraction_matrix[i,j] = yearFraction(day_choose[i],collected_data$MATURITY.DATE[j],freq=2,convention=c("30/360","ACT/ACT","ACT/360","30/360E"))
  }
}
```

```{r}
collected_data <- collected_data %>% dplyr::select(-COUPON, -MONTH.UNTILL.MATURITY)
```

```{r}
yield_1 = matrix('numeric',nrow=10,ncol=10)
for (j in c(1:10)){
  cp = closed_p[,j]
  for(i in c(1:10)){
    yield_1[i,j] <- as.numeric(bond.yield(settle = day_choose[i], mature=collected_data$MATURITY.DATE[j],coupon = collected_data$coupon_final[j],freq = 2,cp[i],convention = c("30/360","ACT/ACT","ACT/360","30/360E"),comp.freq = 2, redemption_value = 100 ))
  }
}
```

```{r}
plot(seq(0.5,5,by=0.5),yield_1[1,], type="l",main="5 years yield to maturity curve", col="black",xlab="Time to Maturity",ylab="Yield",ylim=c(0.025,0.07))
color<-c("chocolate","darkred","darkgreen","gold","deeppink","lightblue","maroon","salmon","yellow","pink")
for(i in c(2:10)){
  lines(seq(0.5,5,by=0.5),yield_1[i,],type="l",col=color[i-1])
}
legend('topright', legend = day_choose, col=c("chocolate","darkred", "darkgreen", "gold", "deeppink", "lightblue", "maroon", "salmon","yellow","pink"), lty=1.18, cex=0.48)
```
```{r}
spot_matrix = matrix('numeric',nrow = 10,ncol = 10)
```

#below I calculate the cash flaw for all the bond base one the function bond.TCU, here use the vector of cash flows
```{r}
cash_bond1 = bond.TCF(day_choose[1],collected_data$MATURITY.DATE[1],collected_data$coupon_final[1],freq=2,
              redemption_value = 100)$cf
cash_bond2 = bond.TCF(day_choose[2],collected_data$MATURITY.DATE[2],collected_data$coupon_final[2],freq=2,
              redemption_value = 100)$cf
cash_bond3 = bond.TCF(day_choose[3],collected_data$MATURITY.DATE[3],collected_data$coupon_final[3],freq=2,
              redemption_value = 100)$cf
cash_bond4 = bond.TCF(day_choose[4],collected_data$MATURITY.DATE[4],collected_data$coupon_final[4],freq=2,
              redemption_value = 100)$cf
cash_bond5 = bond.TCF(day_choose[5],collected_data$MATURITY.DATE[5],collected_data$coupon_final[5],freq=2,
              redemption_value = 100)$cf
cash_bond6 = bond.TCF(day_choose[6],collected_data$MATURITY.DATE[6],collected_data$coupon_final[6],freq=2,
              redemption_value = 100)$cf
cash_bond7 = bond.TCF(day_choose[7],collected_data$MATURITY.DATE[7],collected_data$coupon_final[7],freq=2,
              redemption_value = 100)$cf
cash_bond8 = bond.TCF(day_choose[8],collected_data$MATURITY.DATE[8],collected_data$coupon_final[8],freq=2,
              redemption_value = 100)$cf
cash_bond9 = bond.TCF(day_choose[9],collected_data$MATURITY.DATE[9],collected_data$coupon_final[9],freq=2,
              redemption_value = 100)$cf
cash_bond10 = bond.TCF(day_choose[10],collected_data$MATURITY.DATE[10],collected_data$coupon_final[10],freq=2,
              redemption_value = 100)$cf
```

```{r}
cash_bond1#这里就是看一下选的对不对，记得删了
cash_bond2
cash_bond3
cash_bond4
cash_bond5
cash_bond6
cash_bond7
cash_bond8
cash_bond9
cash_bond10
```

```{r}
spot_1=c()
spot_2=c()
spot_3=c()
spot_4=c()
spot_5=c()
spot_6=c()
spot_7=c()
spot_8=c()
spot_9=c()
spot_10=c()
#第一个bond的只有1个cash
for (i in 1:10){
  stay_time=as.numeric(year_fraction_matrix[i,1])
  spot_1[i]<-log(cash_bond1[1]/as.numeric(price_dirty[i,1]))/stay_time
}
#第二个bond有1个cash
for (i in 1:10){
  stay_time_2=as.numeric(year_fraction_matrix[i,2])
  spot_2[i]<-log(cash_bond2[1]/as.numeric(price_dirty[i,2]))/stay_time_2
}
#第三个bond有3个cash
for (i in 1:10){
  stay_time_3=as.numeric(year_fraction_matrix[i,3])
  remain_3=as.numeric(price_dirty[i,3])-cash_bond3[1]*exp(-1*spot_1[i]*stay_time_3)-cash_bond3[2]*exp(-1*spot_2[i]*stay_time_3)
  spot_3[i]<-log(cash_bond3[3]/remain_3)/stay_time_3
}
#第四个bond有4个cash
for (i in 1:10){
  stay_time_4=as.numeric(year_fraction_matrix[i,4])
  remain_4=as.numeric(price_dirty[i,4])-cash_bond4[1]*exp(-1*spot_1[i]*stay_time_4)-cash_bond4[2]*exp(-1*spot_2[i]*stay_time_4)-cash_bond4[3]*exp(-1*spot_3[i]*stay_time_4)
  spot_4[i]<-log(cash_bond4[4]/remain_4)/stay_time_4
}
#第五个bond有5个cash
for (i in 1:10){
  stay_time_5=as.numeric(year_fraction_matrix[i,5])
  remain_5=as.numeric(price_dirty[i,5])-cash_bond5[1]*exp(-1*spot_1[i]*stay_time_5)-cash_bond5[2]*exp(-1*spot_2[i]*stay_time_5)-cash_bond5[3]*exp(-1*spot_3[i]*stay_time_5) - cash_bond5[4]*exp(-1*spot_4[i]*stay_time_5)
  spot_5[i]<-log(cash_bond5[5]/remain_5)/stay_time_5
}
#第六个bond有6个cash
for (i in 1:10){
  stay_time_6=as.numeric(year_fraction_matrix[i,6])
  remain_6=as.numeric(price_dirty[i,6]) - cash_bond6[1]*exp(-1*spot_1[i]*stay_time_6) - cash_bond6[2]*exp(-1*spot_2[i]*stay_time_6) - cash_bond6[3]*exp(-1*spot_3[i]*stay_time_6) - cash_bond6[4]*exp(-1*spot_4[i]*stay_time_6) - cash_bond6[5]*exp(-1*spot_5[i]*stay_time_6)
  spot_6[i]<-log(cash_bond6[6]/remain_6)/stay_time_6
}
#第七个bond有7个cash
for (i in 1:10){
  stay_time_7=as.numeric(year_fraction_matrix[i,7])
  remain_7=as.numeric(price_dirty[i,7]) - cash_bond7[1]*exp(-1*spot_1[i]*stay_time_7) - cash_bond7[2]*exp(-1*spot_2[i]*stay_time_7) - cash_bond7[3]*exp(-1*spot_3[i]*stay_time_7) - cash_bond7[4]*exp(-1*spot_4[i]*stay_time_7) - cash_bond7[5]*exp(-1*spot_5[i]*stay_time_7) - cash_bond7[6]*exp(-1*spot_6[i]*stay_time_7)
  spot_7[i]<-log(cash_bond7[7]/remain_7)/stay_time_7
}
#第八个bond有8个cash
for (i in 1:10){
  stay_time_8=as.numeric(year_fraction_matrix[i,8])
  remain_8=as.numeric(price_dirty[i,8]) - cash_bond8[1]*exp(-1*spot_1[i]*stay_time_8) - cash_bond8[2]*exp(-1*spot_2[i]*stay_time_8) - cash_bond8[3]*exp(-1*spot_3[i]*stay_time_8) - cash_bond8[4]*exp(-1*spot_4[i]*stay_time_8) - cash_bond8[5]*exp(-1*spot_5[i]*stay_time_8) - cash_bond8[6]*exp(-1*spot_6[i]*stay_time_8) - cash_bond8[7]*exp(-1*spot_7[i]*stay_time_8)
  spot_8[i]<-log(cash_bond8[8]/remain_8)/stay_time_8
}
#第九个bond有9个cash
for (i in 1:10){
  stay_time_9=as.numeric(year_fraction_matrix[i,9])
  remain_9=as.numeric(price_dirty[i,9]) - cash_bond9[1]*exp(-1*spot_1[i]*stay_time_9) - cash_bond9[2]*exp(-1*spot_2[i]*stay_time_9) - cash_bond9[3]*exp(-1*spot_3[i]*stay_time_9) - cash_bond9[4]*exp(-1*spot_4[i]*stay_time_9) - cash_bond9[5]*exp(-1*spot_5[i]*stay_time_9) - cash_bond9[6]*exp(-1*spot_6[i]*stay_time_9) - cash_bond9[7]*exp(-1*spot_7[i]*stay_time_9) - cash_bond9[8]*exp(-1*spot_8[i]*stay_time_9)
  spot_9[i]<-log(cash_bond9[9]/remain_9)/stay_time_9
}
#第十个bond有10个cash
for (i in 1:10){
  stay_time_10=as.numeric(year_fraction_matrix[i,10])
  remain_10=as.numeric(price_dirty[i,10]) - cash_bond10[1]*exp(-1*spot_1[i]*stay_time_10) - cash_bond10[2]*exp(-1*spot_2[i]*stay_time_10) - cash_bond10[3]*exp(-1*spot_3[i]*stay_time_10) - cash_bond10[4]*exp(-1*spot_4[i]*stay_time_10) - cash_bond10[5]*exp(-1*spot_5[i]*stay_time_10) - cash_bond10[6]*exp(-1*spot_6[i]*stay_time_10) - cash_bond10[7]*exp(-1*spot_7[i]*stay_time_10) - cash_bond10[8]*exp(-1*spot_8[i]*stay_time_10) - cash_bond10[9]*exp(-1*spot_9[i]*stay_time_10)
  spot_10[i]<-log(cash_bond10[10]/remain_10)/stay_time_10
}
```

```{r}
whole_spot_matrix = cbind(spot_1, spot_2, spot_3, spot_4, spot_5, spot_6, spot_7, spot_8, spot_9, spot_10)
```

```{r}
plot(seq(0.5,5,by=0.5),whole_spot_matrix[1,], type="l",main="5 years spot rate curve", col="black",xlab="Time to Maturity",ylab="Spot Rate",ylim=c(0,0.2))
color<-c("chocolate","darkred","darkgreen","gold","deeppink","lightblue","maroon","salmon","yellow","pink")
for(i in c(2:10)){
  lines(seq(0.5,5,by=0.5),whole_spot_matrix[i,],type="l",col=color[i-1])
}
legend('topright', legend = day_choose, col=c("chocolate","darkred", "darkgreen", "gold", "deeppink", "lightblue", "maroon", "salmon","yellow","pink"), lty=1.18, cex=0.48)
```


```{r}
one_one_forward = c(10)
one_two_forward=c(10)
one_three_forward=c(10)
one_four_forward=c(10)
for (i in c(1:10))
  one_one_forward[i] = ((1+spot_2[i])^(stay_time_2))-1

for (i in c(1:10))
  one_two_forward[i] = ((1+spot_4[i])^(stay_time_4))/((1+spot_1[i])^(stay_time))-1

for (i in c(1:10))
  one_three_forward[i] = ((1+spot_6[i])^(stay_time_6))/((1+spot_1[i])^(stay_time))-1

for (i in c(1:10))
  one_four_forward[i] = ((1+spot_8[i])^(stay_time_8))/((1+spot_1[i])^(stay_time))-1

forward_matrix_1<-cbind(one_one_forward,one_two_forward,one_three_forward,one_four_forward)
```

```{r}
plot(seq(2,5,by=1),forward_matrix_1[1,], type="l",main="2-5 year forward rate", col="black",xlab="Years",ylab="Forward Rate",ylim=c(0,0.2))
color<-c("chocolate","darkred","darkgreen","gold","deeppink","lightblue","maroon","salmon","yellow","pink")
for(i in c(2:10)){
  lines(seq(2,5,by=1),forward_matrix_1[i,],type="l",col=color[i-1])
}
legend('topright', legend = day_choose, col=c("chocolate","darkred", "darkgreen", "gold", "deeppink", "lightblue", "maroon", "salmon","yellow","pink"), lty=1.18, cex=0.48)
```

```{r}
line1=vector("numeric",9)
line2=vector("numeric",9)
line3=vector("numeric",9)
line4=vector("numeric",9)
line5=vector("numeric",9)
for (i in 1:9)
{
  line1[i]=log(as.numeric(yield_1[i+1,2])/as.numeric(yield_1[i,2]))
  line2[i]=log(as.numeric(yield_1[i+1,4])/as.numeric(yield_1[i,4]))
  line3[i]=log(as.numeric(yield_1[i+1,6])/as.numeric(yield_1[i,6]))
  line4[i]=log(as.numeric(yield_1[i+1,8])/as.numeric(yield_1[i,8]))
  line5[i]=log(as.numeric(yield_1[i+1,10])/as.numeric(yield_1[i,10]))
}

log_yield = data.frame(line1,line2,line3,line4,line5)
covariance_yield = cov(log_yield,log_yield)
print(covariance_yield)
```


```{r}
line1_1=vector("numeric",9)
line2_1=vector("numeric",9)
line3_1=vector("numeric",9)
line4_1=vector("numeric",9)
for (i in 1:9)
{
  line1_1[i]=log(as.numeric(forward_matrix_1[i+1,1])/as.numeric(forward_matrix_1[i,1]))
  line2_1[i]=log(as.numeric(forward_matrix_1[i+1,2])/as.numeric(forward_matrix_1[i,2]))
  line3_1[i]=log(as.numeric(forward_matrix_1[i+1,3])/as.numeric(forward_matrix_1[i,3]))
  line4_1[i]=log(as.numeric(forward_matrix_1[i+1,4])/as.numeric(forward_matrix_1[i,4]))
}

log_forward_matrix = data.frame(line1_1,line2_1,line3_1,line4_1)
covariance_forward = cov(log_forward_matrix,log_forward_matrix)
print(covariance_yield)
```


```{r}
print(eigen(covariance_yield)$values)
print(eigen(covariance_yield)$vectors)
print(eigen(covariance_forward)$values)
print(eigen(covariance_forward)$vectors)                                       
```

